|

### 2024-08-16 README.qmd
delete
repo_prep
stuff
readme

# Example

@@

data <- read_rds(here::here("data", "empirical-plumbeus.Rds"))

>>>>

## Alastair Harry, Ivy Baremore, Andrew Piercy

Published scientific manuscript:

Harry AV, Baremore IE & Piercy AN (2024) Quantifying maternal reproductive output of chondrichthyan fishes. *Canadian Journal of Fisheries and Aquatic Sciences*

![](https://mc06.manuscriptcentral.com/societyimages/cjfas-pubs/scholarOne-CJFAS_en_US.png)

Repository structure

fs::dir_tree()

# Empirical example

@@

data <- read_csv(here::here("data", "empirical-plumbeus.csv"))

### 2024-08-16 rmds/manuscript.Rmd
readme

# Load results
empirical <- read_rds(here("data", "empirical-summary.Rds"))
plumbeus <- read_rds(here("data", "empirical-plumbeus.Rds"))

@@

>>>>

# Load results
empirical <- read_rds(here("data", "empirical-summary.Rds"))
plumbeus <- read_csv(here("data", "empirical-plumbeus.csv"))

@@

# Funding statement

The authors declare no specific funding for this work.
